Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Structural Updates and upload of SoundPulse Logo

:::: {.columns}
::: {.column width="60%"}
<h3>Ever felt like this?</h3>

@@

![](https://media2.giphy.com/media/v1.Y2lkPTc5MGI3NjExeXFwNHV6N3B4cmIzaTY3ajYwYTRkNG95ZWtxdjB5cTE1djRibGRydCZlcD12MV9pbnRlcm5hbF9naWZfYnlfaWQmY3Q9Zw/xT0BKiK5sOCVdBUhiM/giphy.gif){width="90%"}
:::
::::

>>>>

:::: {.columns}
::: {.column .nonincremental width="60%"}
<h3>Ever felt like this?</h3>

@@

![](img/SoundPulseLogo.png){width="100%"}
:::
::::
